flowCore: A Bioconductor software package for high throughput flow cytometry analysis

### 2008-08-15 paper/manuscript.tex
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@33254 bc3139a8-67e5-0310-9ffc-ced21a209358

Through \Rpackage{flowCore}, we have provided the FCM community an
open source, freely available, highly functional, standards compliant
development and analysis platform for high throughput data analysis.
Our intention is to provide a platform for the collaborative
development of new analysis methods that will facilitate the
transition of these new methods to the larger flow community.  Our
experience has been that the collaborative effort we enable for
devising new methodology has been proven beneficial for a number of
different biological and computational biology challenges.  We hope
that our framework will be the foundation for fruitful shared research
by many collaborators from multiple scientific fields and will help
resolve bottlenecks that currently prevent further development and
deployment of FC-HCS to increasingly complex and important scientific
and clinical applications.

>>>>

Through \Rpackage{flowCore}, we have provided the FCM community with
an open source, freely available, highly functional, standards
compliant development and analysis platform for high throughput data
analysis.  Our intention is to provide a platform for the
collaborative development of new analysis methods that will facilitate
the transition of these new methods to the larger flow community.  Our
experience has been that the collaborative effort we enable for
devising new methodology has been proven beneficial for a number of
different biological and computational biology challenges.  We hope
that our framework will be the foundation for fruitful shared research
by many collaborators from multiple scientific fields and will help
resolve bottlenecks that currently prevent further development and
deployment of FC-HCS to increasingly complex and important scientific
and clinical applications.
